\begin{thebibliography}{99}

\bibitem{cdf:recentSusy} {CDF Trilepton Search, 2009, CDF/PUB/EXOTIC/PUBLIC/9817};\\
{\small \tt http://www-cdf.fnal.gov/physics/exotic/r2a/20090521.trilepton\_3fb/Welcome.html}
%\bibitem{cdf:recentSusy1} {``Inclusive Search for Squark and Gluino Production in $p\bar{p}$ Collisions at $\sqrt{s}$ = 1.96-TeV'', Phys.Rev.Lett.102:121801, (2009).}
\bibitem{d0:recentSusy} {``Search for associated production of charginos and neutralinos in the trilepton final state using 2.3 fb$^{-1}$ of data'', Phys. Lett. B 680, 34 (2009).}
%\bibitem{d0:recentSusy1} {``Search for squarks and gluinos in events with jets and missing transverse energy using 2.1 fb$^{-1}$ of ppbar collision data at $sqrt(s)=1.96$ TeV'', 
%Phys. Lett. B 660 , 449 (2008).}

\bibitem{osnote} {``Data driven background estimate for a new physics search with opposite sign dileptons''}, CMS AN-2009/130.

\bibitem{ssnote} {``Data driven background study for new physics searches with same sign dileptons at $\sqrt{s} = 10 $ TeV''}, CMS AN-2009/138.

\bibitem{mcsusy}{\tt https://twiki.cern.ch/twiki/bin/viewauth/CMS/SUSYMCRequirements0911}.

\bibitem{fast10}{\tt https://twiki.cern.ch/twiki/bin/view/CMS/SUSY33XScan}.

\bibitem{ww} {``Prospects for measuring the $WW$ production cross section in $pp$ collisions at $\sqrt s = $10 TeV''}, CMS AN-2009/042 and PAS EWK-09-002.

\bibitem{ttbar} {``Expectations for observation of top quark pair production in the dilepton final state with the early CMS data''}, CMS AN-2009/050 and PAS TOP-09-002.

\bibitem{tcmet} {``Correcting Missing Transverse Energy Using Tracks``} CMS AN-2009/022.

\bibitem{conversionnote} {``Study of photon conversion rejection at CMS''}, CMS AN-2009/159.

\bibitem{glbtrk} {\tt https://hypernews.cern.ch/HyperNews/CMS/get/muon/258.html}.

\bibitem{muonid} {``Muon Identification in CMS''}, CMS AN-2008/098.

\bibitem{vplusj} {\tt https://twiki.cern.ch/twiki/bin/view/CMS/VplusJets}.

\bibitem{fakenote} {``Data-driven methods to estimate the electron and muon fake contributions to lepton analyses''}, CMS AN-2009/041.

\bibitem{cite:cousins} {``Evaluation of three methods for calculating statistical significance when incorporating a systematic uncertainty into a test of the background-only hypothesis for a Poisson process''} arXiv:physics/0702156 [physics.data-an]

\bibitem{cite:conway} {``Interval estimation in the presence of nuisance parameters. 1. Bayesian approach''} arXiv:physics/0409129v1 [physics.data-an]

\bibitem{lep:lepsusyreach}{LEP Susy working group: {\tt http://lepsusy.web.cern.ch/lepsusy/} }

\bibitem{bayes}{\tt http://arxiv.org/pdf/physics/0409129}

\bibitem{victor} {\tt http://arxiv.org/pdf/0906.5016}; \\
{\tt http://indico.cern.ch/contributionDisplay.py?contribId=2\&confId=39042}.

\bibitem{summer09}{\tt https://twiki.cern.ch/twiki/bin/view/CMS/SUSY31XProduction}.


\end{thebibliography}
