\section{Background Contributions}
\label{sec:bkgds}

We are following the same strategy in estimating the background contributions.
Contributions with genuine same-sign isolated lepton pairs are estimated from simulation,
while the contributions from leptons arising from jets (fakes) and from genuine opposite-sign pairs
with a lepton charge misreconstruction (charge flips) are measured in data using control data samples.
The data-driven estimates are described in the next section.
In addition, as a reference, we are using all relevant available simulated samples to get a feeling of the expected yields
from simulation alone.
As will be shown later in Section~\ref{sec:yields}, contributions with genuine same-sign isolated dileptons
are comparable to those estimated from events with fake leptons, while the predictions from charge flips are
relatively low.
These findings are in a fair agreement with direct estimates from simulation.


We use MC to estimate contributions from the following SM production processes with genuine same-sign isolated dileptons:
\begin{itemize}
\item $qqW^\pm W^\pm, WWW, WWZ, WZZ, ZZZ, WW\gamma, t\bar{t}W, t\bar{t}Z, t\bar{t}\gamma$ and double parton $W^\pm W^\pm$ with two real leptons in the final state.
\item $WZ$, $W\gamma^\star$ ($0.25~\GeV < m_{\gamma^\star}<12~\GeV$), and $ZZ$ with two real leptons in the final state.
\item $W\gamma$ with one real lepton and a photon conversion. This background is a priori not estimated by the fake rate method
because the photon is generally isolated. 
%In practice, this background is completely negligible.
\end{itemize}
Details on the sameples used and the corresponding cross sections can be found in Ref.~\cite{ssnote2011}.