\begin{thebibliography}{99}




\bibitem{sspaper2010} 
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  {\it ``Search for new physics with same-sign isolated dilepton 
	events with jets and missing transverse energy at the LHC,''}
  JHEP {\bf 1106}, 077 (2011)
  [arXiv:1104.3168 [hep-ex]].
  %%CITATION = ARXIV:1104.3168;%%

\bibitem{ssnote2011} {{\it ``Search for New Physics with Same-Sign dileptons using the 2011 dataset of CMS''}}, 
  CMS AN-2011/468.

\bibitem{sspaper2011} CMS Collaboration, {{\it ``Search for new physics with same-sign isolated 
	dilepton events with jets and missing energy''}}, 
  CMS PAS SUS-11-010/SUS-11-025, in preparation.

\bibitem{sstop} 
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  {\it ``Search for Same-Sign Top-Quark Pair Production at $\sqrt{s} = 7$~TeV 
	and Limits on Flavour Changing Neutral Currents in the Top Sector,''}
  JHEP {\bf 1108}, 005 (2011)
  [arXiv:1106.2142 [hep-ex]].
  %%CITATION = ARXIV:1106.2142;%%


% \bibitem{BTVPAS2011} CMS Collaboration, {{\it ``Measurement from data of efficiency and mistag rate of 
%	b-tagging algorithms using 2010 data''}}, PAS BTV-11-001 (Submitted)



% \bibitem{CLSxx} {A.L. Read, CERN Report 2000-005 p. 81 (2000).}

% \bibitem{bayesian}{whatever}, some bayesian reference.


% \bibitem{berger}{The same sign top}, {E.~Berger et al.}

% \bibitem{littlehiggs}{ http://arxiv.org/abs/0801.1679}, { $T_{5/3}$ fermion pair production leading to $t\bar{t}W^+W^-$ final state.}



% \bibitem{toro1}{ http://lhcnewphysics.org/b.011.00.r000 }, { Stop anti-stop production proposal by Toro et al. } 

% \bibitem{toro2}{ http://lhcnewphysics.org/b.007.00.r000 }, { $t\bar{t}t\bar{t}$ production via pair production of a neutral color octet resonance by Toro et al. } 

%\bibitem{naturalness1}{http://arxiv.org/abs/hep-ph/9607394},{A.G.Cohen, D.B.Kaplan, A.E.Nelson}

\bibitem{naturalness1} 
  A.~G.~Cohen, D.~B.~Kaplan and A.~E.~Nelson,
  {\it ``The More minimal supersymmetric standard model,''}
  Phys.\ Lett.\ B {\bf 388}, 588 (1996)
  [hep-ph/9607394].
  %%CITATION = HEP-PH/9607394;%%


%\bibitem{naturalness2}{http://arxiv.org/abs/hep-ph/9507282 },{S.Dimopoulos, G.F. Giudice}
\bibitem{naturalness2} 
  S.~Dimopoulos and G.~F.~Giudice,
  {\it ``Naturalness constraints in supersymmetric theories with nonuniversal soft terms,''}
  Phys.\ Lett.\ B {\bf 357}, 573 (1995)
  [hep-ph/9507282].
  %%CITATION = HEP-PH/9507282;%%


%\bibitem{naturalness3}{http://arxiv.org/abs/hep-ph/9512388},{R.Barbieri, G.Dvali, L.Hall}
\bibitem{naturalness3} 
  R.~Barbieri, G.~R.~Dvali and L.~J.~Hall,
  {\it ``Predictions from a U(2) flavor symmetry in supersymmetric theories,''}
  Phys.\ Lett.\ B {\bf 377}, 76 (1996)
  [hep-ph/9512388].
  %%CITATION = HEP-PH/9512388;%%


%\bibitem{naturalness4}{http://arxiv.org/abs/1110.6926},{``Natural SUSY Endures''}
\bibitem{naturalness4} 
  M.~Papucci, J.~T.~Ruderman and A.~Weiler,
  {\it ``Natural SUSY Endures,''}
  arXiv:1110.6926 [hep-ph].
  %%CITATION = ARXIV:1110.6926;%%



% \bibitem{stopVirtual}{http://arxiv.org/abs/0901.3367 , http://arxiv.org/abs/1101.1963},{ gluino with virtual stop}
\bibitem{stopVirtual} 
  B.~S.~Acharya, P.~Grajek, G.~L.~Kane, E.~Kuflik, K.~Suruliz and L.~-T.~Wang,
  {\it ``Identifying Multi-Top Events from Gluino Decay at the LHC,''}
  arXiv:0901.3367 [hep-ph].
  %%CITATION = ARXIV:0901.3367;%%

\bibitem{stopVirtualPRD} 
  G.~L.~Kane, E.~Kuflik, R.~Lu and L.~-T.~Wang,
  {\it ``Top Channel for Early SUSY Discovery at the LHC,''}
  Phys.\ Rev.\ D {\bf 84}, 095004 (2011)
  [arXiv:1101.1963 [hep-ph]].
  %%CITATION = ARXIV:1101.1963;%%


%\bibitem{stopReal}{http://arxiv.org/abs/hep-ph/0512284 },{gluino with stop real}
\bibitem{stopReal} 
  S.~Kraml and A.~R.~Raklev,
  {\it ``Same-sign top quarks as signature of light stops at the LHC,''}
  Phys.\ Rev.\ D {\bf 73}, 075002 (2006)
  [hep-ph/0512284].
  %%CITATION = HEP-PH/0512284;%%


%\bibitem{sbottom}{},{}
%\bibitem{gluinosbottom}{},{}

%\bibitem{wacker}{http://arxiv.org/abs/1110.6443},{Wacker et al. sms paper}
\bibitem{wacker} 
  R.~Essig, E.~Izaguirre, J.~Kaplan and J.~G.~Wacker,
  {\it ``Heavy Flavor Simplified Models at the LHC,''}
  arXiv:1110.6443 [hep-ph].
  %%CITATION = ARXIV:1110.6443;%%


%\bibitem{sgluons}{http://arxiv.org/abs/0810.3919},{``Seeking Sgluons''}
\bibitem{sgluons} 
  T.~Plehn and T.~M.~P.~Tait,
  {\it ``Seeking Sgluons,''}
  J.\ Phys.\ G G {\bf 36}, 075001 (2009)
  [arXiv:0810.3919 [hep-ph]].
  %%CITATION = ARXIV:0810.3919;%%

%\bibitem{colorOctetScalars}{http://arxiv.org/abs/0710.3133},{``Color-octet scalara at the LHC''}
\bibitem{colorOctetScalars} 
  M.~Gerbush, T.~J.~Khoo, D.~J.~Phalen, A.~Pierce and D.~Tucker-Smith,
  {\it ``Color-octet scalars at the CERN LHC,''}
  Phys.\ Rev.\ D {\bf 77}, 095003 (2008)
  [arXiv:0710.3133 [hep-ph]].
  %%CITATION = ARXIV:0710.3133;%%




%\bibitem{mxflv1}{http://arxiv.org/abs/0711.3193},{``Models and Phenomenology of Maximal Flavor Violation''}
\bibitem{mxflv1} 
  S.~Bar-Shalom and A.~Rajaraman,
  {\it ``Models and phenomenology of maximal flavor violation,''}
  Phys.\ Rev.\ D {\bf 77}, 095011 (2008)
  [arXiv:0711.3193 [hep-ph]].
  %%CITATION = ARXIV:0711.3193;%%

%\bibitem{mxflv2}{http://arxiv.org/abs/0803.3795},
%	{``Collider Signals of Maximal Flavor Violation: Same-Sign Leptons from Same-Sign Tops at the Tevatron''}
\bibitem{mxflv2} 
  S.~Bar-Shalom, A.~Rajaraman, D.~Whiteson and F.~Yu,
  {\it ``Collider Signals of Maximal Flavor Violation: 
	Same-Sign Leptons from Same-Sign Tops at the Tevatron,''}
  Phys.\ Rev.\ D {\bf 78}, 033003 (2008)
  [arXiv:0803.3795 [hep-ph]].
  %%CITATION = ARXIV:0803.3795;%%

%\bibitem{mxflv3}{http://arxiv.org/abs/0809.4903},{CDF search for MxFlv}
\bibitem{mxflv3} 
  T.~Aaltonen {\it et al.}  [CDF Collaboration],
  {\it ``Search for Maximal Flavor Violating Scalars in 
	Same-Charge Lepton Pairs in $p \bar{p}$ Collisions at $\sqrt{s}$ = 1.96-TeV,''}
  Phys.\ Rev.\ Lett.\  {\bf 102}, 041801 (2009)
  [arXiv:0809.4903 [hep-ex]].
  %%CITATION = ARXIV:0809.4903;%%

\bibitem{T1tttt} D.~Alves {\it et al.}, {\it Simplified Models for LHC New
Physics Searches}, arxiv:1105.2838; this is the model of Section IV.E
with ``topology (B+B)''. 




%\bibitem{fcnczprime}{theory motivating our same sign top paper in 2010},{need to fill this in}
\bibitem{fcnczprime} 
  E.~L.~Berger, Q.~-H.~Cao, C.~-R.~Chen, C.~S.~Li and H.~Zhang,
  {\it ``Top Quark Forward-Backward Asymmetry and Same-Sign Top Quark Pairs,''}
  Phys.\ Rev.\ Lett.\  {\bf 106}, 201801 (2011)
  [arXiv:1101.5625 [hep-ph]].
  %%CITATION = ARXIV:1101.5625;%%


%\bibitem{t53}{doi:10.1088/1126-6708/2008/06/026.},
%	{R. Contino and G. Servant, Discovering the top partners at the LHC using same-sign dilepton final states, JHEP 06 (2008) 026.}
\bibitem{t53} 
  R.~Contino and G.~Servant,
  {\it ``Discovering the top partners at the LHC using same-sign dilepton final states,''}
  JHEP {\bf 0806}, 026 (2008)
  [arXiv:0801.1679 [hep-ph]].
  %%CITATION = ARXIV:0801.1679;%%


%\bibitem{topcomp1}{http://arxiv.org/abs/0712.3057},{``Top Compositeness at the Tevatron and LHC''}
\bibitem{topcomp1} 
  B.~Lillie, J.~Shu and T.~M.~P.~Tait,
  {\it ``Top Compositeness at the Tevatron and LHC,''}
  JHEP {\bf 0804}, 087 (2008)
  [arXiv:0712.3057 [hep-ph]].
  %%CITATION = ARXIV:0712.3057;%%


%\bibitem{topcomp2}{http://arxiv.org/abs/0806.3247},{``Top Quark Compositeness: Feasibility and Implications''}
\bibitem{topcomp2} 
  A.~Pomarol and J.~Serra,
  {\it ``Top Quark Compositeness: Feasibility and Implications,''}
  Phys.\ Rev.\ D {\bf 78}, 074026 (2008)
  [arXiv:0806.3247 [hep-ph]].
  %%CITATION = ARXIV:0806.3247;%%


%\bibitem{topcomp3}{http://arxiv.org/abs/0901.3808},{``Manifestations of Top Compositeness at Colliders''}
\bibitem{topcomp3} 
  K.~Kumar, T.~M.~P.~Tait and R.~Vega-Morales,
  {\it ``Manifestations of Top Compositeness at Colliders,''}
  JHEP {\bf 0905}, 022 (2009)
  [arXiv:0901.3808 [hep-ph]].
  %%CITATION = ARXIV:0901.3808;%%




\bibitem{BTV11003} CMS Collaboration, {{\it ``Measurement of the b-tagging efficiency using \ttbar\ events''}}, 
	PAS BTV-11-003, in preparation.

\bibitem{btvSyst} M.~Narain for BTV POG, \url{https://indico.cern.ch/getFile.py/access?contribId=0&resId=1&materialId=slides&confId=163892}


\bibitem{frmethod}{{\it ``Fake Rates for Dilepton Analyses''}}, CMS AN-2010/257.


\bibitem{d0:fwtop} {D0 Collaboration, ``First measurement of the forward-backward charge asymmetry in top quark pair production'', Phys.Rev.Lett.100:142002, (2008)}

\bibitem{cdf:fwtop1} {CDF Collaboration, ``Forward-Backward Asymmetry in Top Quark Production in $p\bar{p}$ Collisions at $sqrt{s}=1.96$ TeV'', Phys.Rev.Lett.101:202001, (2008)}

\bibitem{cdf:fwtop2} {CDF Collaboration, ``Evidence for a Mass Dependent Forward-Backward Asymmetry in Top Quark Pair Production'', arXiv:1101.0034, (2011)}

% \bibitem{berger} {Ed.Berger et. al, ``Top Quark Forward-Backward Asymmetry and Same-Sign Top Quark Pairs'', arXiv:1101.5625, (2011)}

\bibitem{Buckley} {M.R. Buckley et. al, ``Light Z' Bosons at the Tevatron'', arXiv:1103.6035, (2011)}

\bibitem{Gresham} {Moira I. Gresham et. al, ``On Models of New Physics for the Tevatron Top AFB'', arXiv:1103.3501, (2011)}

\bibitem{zoltan} {Z.Ligeti et. al, ``Explaining the t tbar forward-backward asymmetry without dijet or flavor anomalies'', arXiv:1103.2757, (2011)}

% \bibitem{hills} {C.T Hill, Phys. Lett. B345, 483 (1995)}

% \bibitem{others1} {R.S. Chivukula, E.H. Simmons and J. Terning, Phys.Lett.B331,383 (1984); D.J. Muller and S. Nandi, Phys.Lett.B383,345 (1996); E. Malkawi, T. Tait 
% and C.-P. Yuan, Phys.Lett.B385,304 (1996); K. Lane and E.Eichten, Phys.Lett.B433,96 (1998); C.T. Hill, Phys.Rev.D59,075003 (1999); H. Georgi and A.K. Grant, 
% Phys.Rev.D63,015001 (2001).}

\bibitem{Cao} {Q.H. Cao et. al. Phys.Rev.D81, 114004 (2010)}

\bibitem{ttAN} {CMS AN-2011/137}

\bibitem{sstopatlas} ATLAS Collaboration, 
``Search for anomalous production of prompt like-sign muon 
pairs and constraints on physics beyond the Standard Model
with the ATLAS detector",   [arXiv:1201.1091 [hep-ex]], submitted to 
\textit{Phys. Rev. D}.

\bibitem{cdfth2} {J. A. Aguilar-Saavedra, 
 ``Effective four-fermion operators in top physics: a roadmap'', 
 Nucl. Phys. B843 (2011), arXiv:1008:3562.}

\bibitem{cdflimit} {``Search for like-sign top quark pair production at CDF with 6.1 fb$^{-1}$''}, CDF/PHYS/EXO/PUBLIC/10466, 
{\tt http://www-cdf.fnal.gov/physics/exotic/r2a/20110407.samesigndileptons/sstops.pdf}

\bibitem{simplifiedModel}{ http://lhcnewphysics.org/l.006.00.r000},{ Simplified model by Felix Yu, UCI}

\bibitem{susyssbtags} { http://arxiv.org/abs/hep-ph/0512284},{SUSY Gluinos to light stop}

\bibitem{susyssbtags2} { http://arxiv.org/abs/1004.2256},{more SUSY Gluinos to light stop}






\end{thebibliography}







