\section{Conclusion}
\label{sec:conclusion}
In conclusion, the first search using same-sign dileptons with $b$-jets and \met~~has 
been presented. In the
proton-proton collision data sample corresponding to an integrated luminosity of 
 \intLumi~at $\sqrt{s}$ = 7 TeV,
no significant deviations from the Standard Model expectations are observed. 
We use this data to set 95\% CL. on the
number of observed events for a number of plausible signal regions
defined in terms of requirements in \met and $H_T$, the number of
$b$-tagged jets (2 or 3), and also the sign of the leptons (only positive dileptons
or both positive and negative dileptons).
We also provide enough information so that interested phenomenologists
could interpret our limits in their favorite new physics models.

In addition, we set limits on the parameter space of six new physics models:
\begin{enumerate}
\item A model with a $Z'$ vector boson with flavor violating couplings to $u-$ and $t$-quarks.

\item A model with a neutral scalar with flavor violating couplings to $u-$ and $t$-quarks.

\item A SUSY model of stop production from two body gluino decays: 
$pp \to \widetilde{g} \widetilde{g}$ followed by
$\widetilde{g} \to t\widetilde{t}$ and $\widetilde{t} \to t \chi_1^0$.

\item A SUSY model of stop pair production from three body gluino decays:
$pp \to \widetilde{g} \widetilde{g}$ followed by
$\widetilde{g} \to t\widetilde{t}\chi_1^0$.

\item A SUSY model of sbottom pair production: $pp \to \tilde{b}\tilde{b}$ followed
by $\tilde{b} \to t\chi^{-}$ and $\chi^{-} \to W^- \chi_1^0$.

\item A SUSY model of sbottom production from gluino decays:
$pp \to \widetilde{g} \widetilde{g}$ followed by
$\widetilde{g} \to \widetilde{b}b$,
$\widetilde{b} \to t\chi^-$, and $\chi^{-} \to W^- \chi_1^0$.
\end{enumerate}

And that's all for now.
