\section{Searches for Specific Models}
\label{sec:stampCollecting}

Our signature, two isolated same-sign leptons plus, at least two b-tagged jets, and \met, 
is common to many different new physics scenarios, as well as standard model $t\bar{t}W$ production.

Here we refine our analysis to define dedicated signal regions for a few of these scenarios,
and provide 95\% C.L. upper limits on their respective model parameter space.

{\it We expect to explore the following models for the final paper:}

\begin{itemize}
\item Top pair production via t-channel $Z^\prime$ exchange
as proposed by~\cite{berger} and searched for by CMS with 2010 data~\cite{sstop}. This is in some ways a minimal 
model for our purposes, as it produces nothing other than same sign dileptons, two b-jets, and moderate \met\ typical
for two leptonic W decays.
\item A simplified model for same-sing top pair production as suggested in~\cite{simplifiedModel}. 
The production mechanisms here range from t-channel uu-scattering to $tt$, as in the previous example, to
$tt\bar{u}\bar{u}$. The main difference to the previous model is different kinematics of the top quarks
due to an intermeditate resonance $\eta^0\to t \bar{u}$ decay. The mass of the $\eta^0$ is the main parameter
in the simplified model.
\item Standard model $t\bar{t}W$ production. Here the final state is same sign dileptons, two neutrinos, 
i.e. moderate \met, plus one top quark that decays generically.
\item $T_{5/3}$ fermion from Little Higgs models as suggested in~\cite{littlehiggs} lead to a $t\bar{t}W^+W^-$ final state, thus providing one additional W over the previous example.
\item SUSY gluino pair production with the gluino decaying to top and stop as suggested in~\cite{susyssbtags}\cite{susyssbtags2}. Depending on stop mass, this leads to a final state of either 
$t\bar{t}t\bar{t}$ plus \met , or $tt\bar{Q}\bar{Q}$ 
plus \met\ with $Q$ being charm or beauty, and charge conjugates, as sources for the same sign dilepton plus 
two btags plus \met. Independent of stop mass, final states with same sign dileptons plus four heavy flavor quarks
plus \met\ are produced.
\end{itemize}

{\it We will fill this in as we generate the samples, and figure out what minor changes to our baseline cuts each model
requires to be sort of moderately optimized. In general, we expect changes in lepton $p_T$, \met, $H_T$, and possibly
jet $p_T$ requirements, but no object selection changes.}

{\it Below are some other ideas being tossed around for other analyses, that we might be competitive with in
some parts of the parameter space.}

\begin{itemize}
\item Pair production of heavy flavored squarks and their anti-squarks~\cite{toro1}. In its simplest form, this just gives 
$t\bar{t}$ plus \met , $t\bar{b}$ plus \met , or $b\bar{b}$ plus \met , and is thus not relevant for us. It's being looked at
in the context of the \met\ plus jets analyses. 
However, there is a variant for which the stop decay proceeds through an intermediate neutralino that decays to W plus
chargino, with the chargino being close to degenerate in mass with the neutralino LSP. In this case,
the stop anti-stop production mechanism results in a $t\bar{t}W^+W^-$ plus \met\ final state. This is thus the same 
final state as the $T_{5/3}$ pair production mentioned above, except with two additional LSPs. 
There may be parts of the parameter space for which the LSP is very light, thus not providing enough \met\ for the 
\met\ plus jets analyses to see it, or the opposite extreme, where the LSP is so massive, that the Q value of the decays
leads to LSPs at rest in the labframe, and thus little \met . Not sure to what extend these corners of phase space are
big enough to pursue.
\item Pair production of color octet neutral scalars that each decay to $t\bar{}t$~\cite{toro2}, thus leading to a final state
similar as the the SUSY gluino pair production, except with no additional \met\ beyond the neutrinos from leptonic
W decay. This might thus be possibly missed by the usual \met\ plus jets analyses because it doesn't have enough \met .
It might be a target for us more than them.
\end{itemize}
