\documentclass{cmspaper}
\usepackage{graphicx}
\usepackage{appendix}
\usepackage{rotate}
\usepackage{relsize}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}

\newcommand{\met} {\ensuremath{E\!\!\!\!/_T}}
\newcommand{\ttbar} {\ensuremath{t\bar{t}~}}
\newcommand{\ptll} {\ensuremath{P_T(\ell\ell)}}
\newcommand{\ptllres} {\ensuremath{P^{\rm res}_T(\ell\ell)}}

\begin{document}

%==============================================================================
% title page for many authors
%
\begin{titlepage}
\title{Interpreting CMS data in the phenomenological MSSM}

  \begin{Authlist}
    Maurizio Pierini
    \Instfoot{cern}{CERN}    
    Maria Spiropulu
    \Instfoot{caltech}{CERN \& California Institute Of Technology, Pasadena}    
    Filip Moortgat, Luc Pape
    \Instfoot{eth}{ETH, Zurich, Switzerland}
    Joseph Lykken
    \Instfoot{fnal}{Fermi National Accelerator Laboratory, Batavia, Illinois}
    Harrison Prosper, Sezen Sekmen
    \Instfoot{fsu}{Florida State University, Tallahassee}
    Sabine Kraml
    \Instfoot{lpsc}{LPSC Grenoble, France}
    Sanjay Padhi
    \Instfoot{ucsd}{University of California, San Diego}
    
  \end{Authlist}

\begin{abstract}
We interpret the data taken with the CMS detector during the 7 TeV LHC run within the phenomenological MSSM (pMSSM). 
The pMSSM is a 19-dimensional parametrization of the MSSM that captures most of its phenomenological features. The 19-dimensional model
encompasses, and goes beyond, a broad range of more constrained SUSY models (such as the CMSSM). 
Using profile likelihoods, we examine the influence of each of the 
19 parameters and determine to which parameters 
(and predicted observables) the current CMS data are most sensitive. 
We provide constraints on quantities sensitive to hadronic as well as multi-lepton final states, 
based on the 2010 CMS data-set corresponding to 35~pb$^{-1}$ of integrated luminosity.
In contrast to constraints derived for particular SUSY breaking schemes 
such as the CMSSM, our results provide more generic conclusions on how the current 
data constrain the MSSM. 
Moreover, while the focus of this note is the 
MSSM, the approach we describe is applicable to \emph{any} multi-parameter model.
\end{abstract}
\end{titlepage}

\input{intro.tex}
\input{motivation.tex}
\input{model.tex}
%\input{limit.tex}
\input{analysis.tex}
\input{results.tex}
\input{conclusion.tex}

\section*{Acknowledgements}

We thank JoAnne Hewett and Thomas G. Rizzo for providing us the 6K pMSSM points used in this analysis.



% ---- references ----
%\bibliographystyle{h-physrev}
%\bibliography{pmssm}
\clearpage
\input{pmssmbbl.tex}

% ---- appendix ----
\clearpage
\appendices
\section*{Appendices}
\input{cmsdelphescomp.tex}
\clearpage
\input{statistics.tex}

\end{document}
