\documentclass[12pt,aps,preprint,nofootinbib]{revtex4}

\usepackage{graphicx}
\usepackage{cancel}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{times}
\usepackage{epsfig}
\usepackage{color}
\usepackage{appendix}

\def\lsim{\mathrel{\raise.3ex\hbox{$<$\kern-.75em\lower1ex\hbox{$\sim$}}}}
\def\gsim{\mathrel{\raise.3ex\hbox{$>$\kern-.75em\lower1ex\hbox{$\sim$}}}}

\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}

\def\ptmiss{\cancel{p}_{T}}
\def\etmiss{\cancel{E}_{T}}

\def\dm{\Delta M}
\def\mi{M_1}
\def\mii{M_2}
\def\miii{M_3}
%\def\mg{m_{\tilde g}}
\def\mg{M_3}
\def\mf{m_{\tilde f}}
\def\mlsp{M_{LSP}}

%
\def\lsp{{\chi^0_1}}
\def\none{{\chi^0_1}}
\def\ntwo{{\chi^0_2}}
\def\ni{{\chi^0_i}}
\def\cone{{\chi^\pm_1}}
\def\ctwo{{\chi^\pm_2}}
\def\ci{{\chi^\pm_i}}
\def\mnone{M_{\chi^0_1}}
\def\mntwo{M_{\chi^0_2}}
\def\mni{M_{\chi^0_i}}
\def\mcone{M_{\chi^\pm_1}}
\def\mctwo{M_{\chi^\pm_2}}
\def\mw{M_W}
\def\mz{M_Z}
\def\s{\tilde}
%

\def\nn{\noindent}
\def\non{\nonumber}
\def\ie{{\it i.e.}}
\def\eg{{\it e.g.}}
\def\etc{{\it etc}}
\def\etal{{\it et al.}}
\def\ibid{{\it ibid}.}
\def\tev{\,{\rm TeV}}
\def\gev{\,{\rm GeV}}
\def\mev{\,{\rm MeV}}
\def\ev{\,{\rm eV}}
\def\to{\rightarrow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%\preprint{~~MADPH-10-1556}
\preprint{~~CERN-PACC-1101}

\title{Interpreting CMS data in the phenomenological MSSM}

\author{Sabine Kraml$^{\bf a}$}
\email{sabine.kraml@lpsc.in2p3.fr}

\author{Joseph Lykken$^{\bf b}$}
\email{jlykken@gmail.com}

\author{Filip Moortgat$^{\bf c}$}
\email{filip.moortgat@cern.ch}

\author{Sanjay Padhi$^{\bf d}$}
\email{sanjay.padhi@cern.ch}

\author{Luc Pape$^{\bf c}$}
\email{luc.pape@cern.ch}

\author{Maurizio Pierini$^{\bf e}$}
\email{maurizio.pierini@cern.ch}

\author{Harrison Prosper$^{\bf f}$}
\email{harry@hep.fsu.edu}

\author{Sezen Sekmen$^{\bf f}$}
\email{ssekmen@mail.cern.ch}

\author{Maria Spiropulu$^{\bf e,g}$}
\email{smaria@cern.ch}

\affiliation{
$^{\bf a}$  LPSC Grenoble, France\\
$^{\bf b}$  FNAL, Batavia, Illinois, USA\\
$^{\bf c}$  ETH, Zurich, Switzerland\\
$^{\bf d}$  University of California, San Diego, USA\\
$^{\bf e}$  CERN, Switzerland\\
$^{\bf f}$  Florida State University, Tallahassee, USA\\
$^{\bf g}$  California Institute Of Technology, USA
}
\begin{abstract}
We interpret within the phenomenological MSSM (pMSSM) the data taken with the CMS detector during the 7 TeV LHC run.  
The pMSSM is a 19-dimensional parametrization of the MSSM that captures most of 
its phenomenological features. The 19-dimensional model
encompasses, and goes beyond, a broad range of more constrained SUSY models (such as the CMSSM). 
Using profile likelihoods, we examine the influence of each of the 
19 parameters and determine to which parameters 
(and predicted observables) the current CMS data are most sensitive. 
We provide constraints on quantities sensitive to hadronic as well as multi-lepton final states, 
based on the 2011 CMS data-set corresponding to $\approx$1~fb$^{-1}$ of integrated luminosity.
In contrast to constraints derived for particular SUSY breaking schemes 
such as the CMSSM, our results provide more generic conclusions on how the current 
data constrain the MSSM. Moreover, while the focus of this study is the 
MSSM, the approach we describe is applicable to \emph{any} multi-parameter model.
\end{abstract}

\maketitle

\input{intro.tex}
\input{motivation.tex}
\input{model.tex}
%\input{limit.tex}
\input{analysis.tex}
\input{results.tex}
\input{conclusion.tex}

\section*{Acknowledgements}
We thank ..

\clearpage
\input{resultsfigs.tex}


\newpage

\input{pmssmbbl.tex}
% ---- appendix ----
\clearpage
\appendices
\section*{Appendices}
\input{cmsdelphescomp.tex}
\clearpage
\input{statistics.tex}


\end{document}


